### 2021-10-29 chapters/programming_languages/programming_languages.tex
add : rpc figures

\chapter{The Energy footprints of programming languages}
\label{chapter:porgramming_langauges}
In this chapter we will dicuss the impact of the choice of the programming language on the energy consumption of the software.

\import{chapters/programming_languages/}{challanges}
\import{chapters/programming_languages/}{microbenchmarks}
\import{chapters/programming_languages/}{conclusion}
\import{chapters/programming_languages/}{rpc}
\import{chapters/programming_languages/}{web_frameworks}

>>>>

\chapter{The Energy footprints of programming languages}
\label{chapter:porgramming_langauges}
In this chapter we will dicuss the impact of the choice of the programming language on the energy consumption of the software.
To do so we suggest to start with the general micro benchmarking and see how each programming languages interact with the CPU/ Memory

\import{chapters/programming_languages/}{challanges}
\import{chapters/programming_languages/}{microbenchmarks}
As we have seen in the previous chapter, one of the most important feature of a test is to be \textbf{representative}. Therefore, we extend this study to some reallife use case. The sections belows will provide two study cases.
\import{chapters/programming_languages/}{rpc}
\import{chapters/programming_languages/}{web_frameworks}
\import{chapters/programming_languages/}{conclusion}
